### 2023-09-11 3.Design/activation.tex
Minor details have been changed in the files
added  w and l explain for af
onchip area begin + timediagram for memcell
Moved table's caption to the bottom
Worked on xbar + new package for refs + cleaning repo

\begin{table}[H]
  \centering
  \caption{Circuits parameters}
  \begin{tabular}{|c|c|c|}
    \hline
    \rowcolor{gray}
    Parameter & Sigmoid & \ac{tanh} \\
    \hline
    $V_1$ & \multicolumn{2}{c|}{$1.1V$}\\
    \hline
    $V_2$ & \multicolumn{2}{c|}{$635mV$}\\
    \hline
    $V_3$ & $0.8V$ & $550mV$\\
    \hline
    $i_{dc}$ & \multicolumn{2}{c|}{$150uA$}\\
    \hline
    $w$ & \multicolumn{2}{c|}{$900nm$}\\
    \hline
    $l$ & \multicolumn{2}{c|}{$60nm$}\\
    \hline
    $R_1$ & \multicolumn{2}{c|}{$5k\Omega$}\\
    \hline
    $R_2$ & \multicolumn{2}{c|}{$10k\Omega$}\\
    \hline
    $R_3$ & $2k\Omega$ & $4k\Omega$\\
    \hline
  \end{tabular}
  \label{tab:afPar}
\end{table}

@@

The circuit used is the same as the one in \cite{thesisRef}, the circuit is the one shown in figure \ref{fig:afCircuit}. The technology used being different, all the parameters had to be determined empirically to best fit a sigmoid shape. The parameters can be found in table \ref{tab:afPar}.

@@

\begin{equation}
  A_{af}=2\cdot A_{R_1} + 2\cdot A_{nmos} + 5\cdot A_{R_2} + A_{R_3} +2\cdot A_{opAmp}
\end{equation}
With $A_{nmos} = w\cdot l = 9\cdot 10^{-7} \cdot 6 \cdot 10^{-8} = 5.4 \cdot 10^{-14} m^2$
TODO : Finish calc

@@

\subsection{Results}

This circuit outputs a voltage that depends on the input voltage passed on. The relation between the two is shown in figure \ref{fig:afGraph}. The graph also shows the \ac{RMSE} of each graph compared to the ideal result.

Note that the actual output of the circuit in figure \ref{fig:afCircuit} is inverted arround $V_{cm}$ a simple circuit such as the one shown in  (TODO show circuit in annex) does inverts the

>>>>

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|}
    \hline
    \rowcolor{gray}
    Parameter & Sigmoid & \ac{tanh} \\
    \hline
    $V_1$ & \multicolumn{2}{c|}{$1.1V$}\\
    \hline
    $V_2$ & \multicolumn{2}{c|}{$635mV$}\\
    \hline
    $V_3$ & $0.8V$ & $550mV$\\
    \hline
    $i_{dc}$ & \multicolumn{2}{c|}{$150uA$}\\
    \hline
    $w$ & \multicolumn{2}{c|}{$900nm$}\\
    \hline
    $l$ & \multicolumn{2}{c|}{$60nm$}\\
    \hline
    $R_1$ & \multicolumn{2}{c|}{$5k\Omega$}\\
    \hline
    $R_2$ & \multicolumn{2}{c|}{$10k\Omega$}\\
    \hline
    $R_3$ & $2k\Omega$ & $4k\Omega$\\
    \hline
  \end{tabular}
  \caption{Circuits parameters}
  \label{tab:afPar}
\end{table}

Here, $w$ and $l$ are, respectively, the width and length of the two NMOS of the circuit.

@@

The circuit used is the same as the one in \cite{thesisRef}, the circuit is the one shown in \cref{fig:afCircuit}. The technology used being different, all the parameters had to be determined empirically to best fit a sigmoid shape. The parameters can be found in \cref{tab:afPar}.

@@

\begin{equation}
  A_{af}=2\cdot A_{R_1} + 2\cdot A_{CMOS} + 5\cdot A_{R_2} + A_{R_3} +2\cdot A_{opAmp}
\end{equation}
With $A_{CMOS} = w\cdot l = 9\cdot 10^{-7} \cdot 6 \cdot 10^{-8} = 5.4 \cdot 10^{-14} m^2$
TODO : Finish calc

@@

\subsection{Usage}

This circuit outputs a voltage that depends on the input voltage passed on. The relation between the two is shown in \cref{fig:afGraph}. The graph also shows the \ac{RMSE} of each graph compared to the ideal result.

Note that the actual output of the circuit in \cref{fig:afCircuit} is inverted arround $V_{cm}$ a simple circuit such as the one shown in  (TODO show circuit in annex) does inverts the

### 2023-09-11 3.Design/crossbar.tex
Worked on xbar + new package for refs + cleaning repo

The crossbar circuit has already been explained in the section \ref{sec:crossbar}. This section describes how the crossbar circuit is actually implemented. The final circuit is the one in figure \ref{fig:xbarCircuit}.

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{crossbar/crossbarUse}
  \caption{Crossbar circuit used in the final system}
  \label{fig:xbarCircuit}
\end{figure}

@@

\begin{itemize}
  \item It doubles the range of weights
  \item It allows to easily use negative weights
\end{itemize}

This design is the one that is used in \cite{doubleMem}. Let's assume that a given memristor has a resistance range of $R\in[R_{min},R_{max}]$, that means it's conductance range is $\sigma \in [\sigma_{min},\sigma_{max}]$ (with $\sigma_{min}= \frac{1}{R_{max}}$ and $\sigma_{max}= \frac{1}{R_{min}}$). The use of a design such as the one specifically displayed if figure TODO. It works with two \ac{opAmp}.

\begin{equation}
  V_{opAmp1}=-R\cdot i_+
\end{equation}
\begin{equation}
  i_{R_f}=i_-+\frac{V_{opAmp1}}{R}=i_--i_+
\end{equation}
With $i_{opAmp}=0A$ because we assume an ideal \ac{opamp}.
\begin{equation}
  V_{opAmp2}=V_{out}=-R_f\cdot(i_--i_+)=R_f\cdot(i_+-i_-)=R_f\cdot\sum_{k=0}^n(\sigma_{k+}-\sigma_{k-})\cdot x_k
\end{equation}
With $i_+=\sum_{k=0}^n\sigma_{k+}\cdot x_k$ and $i_-=\sum_{k=0}^n\sigma_{k-}\cdot x_k$.

>>>>

The crossbar circuit theory has already been explained in the \cref{sec:crossbar}. This section describes how the crossbar circuit is actually implemented. The final circuit is the one in \cref{circt:xbar}.

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{crossbar/crossbarUse}
  \caption{Crossbar circuit used in the final system}
  \label{circt:xbar}
\end{figure}

@@

\begin{itemize}
  \item It doubles the range of weights (\cref{tab:synapses})
  \item It allows to easily use negative weights, as this design simply allows the output values to be centered around $V_{cm}$ to be compliant with the standard set in \cref{tab:valConv}.
\end{itemize}

This design is the one that is used in \cite{doubleMem}. Let's assume that a given memristor has a resistance range of $R\in[R_{min},R_{max}]$, that means it's conductance range is $\sigma \in [\sigma_{min},\sigma_{max}]$ (with $\sigma_{min}= \frac{1}{R_{max}}$ and $\sigma_{max}= \frac{1}{R_{min}}$). This design works using two \ac{opAmp} connected to $V_{cm}$ with the positive pin and the negative pin to the output of the crossbar array. \Cref{eq:doubleMem0,eq:doubleMem1,eq:doubleMem2} are describing how this architecture works.

\begin{equation}
  \label{eq:doubleMem0}
  V_{opAmp1}=-R\cdot i_+
\end{equation}
\begin{equation}
  \label{eq:doubleMem1}
  i_{R_f}=i_-+\frac{V_{opAmp1}}{R}=i_--i_+
\end{equation}
With $i_{opAmp}=0A$ because we assume an ideal \ac{opamp}.
\begin{equation}
  \label{eq:doubleMem2}
  V_{opAmp2}=V_{out}=-R_f\cdot(i_--i_+)=R_f\cdot(i_+-i_-)=R_f\cdot\sum_{k=0}^n(\sigma_{k+}-\sigma_{k-})\cdot x_k
\end{equation}
With $i_+=\sum_{k=0}^n\sigma_{k+}\cdot x_k$ and $i_-=\sum_{k=0}^n\sigma_{k-}\cdot x_k$.

### 2023-09-11 3.Design/memcell.tex
Worked on xbar + new package for refs + cleaning repo

The circuit is shown in figure \ref{fig:memcellCircuit}. The value/voltage is trapped in the capacitor using \ac{CMOS} switches.

@@

The cirucit has a two \ac{CMOS} switches design to avoid voltage leakage through the swicthes. The system has voltage leakage when only one \ac{CMOS} swicth, and thus leads to a large memory leak. This is due to the high voltage difference between the two sides of the \ac{CMOS} swicth. Using two \ac{CMOS} switches allows for this difference to be mitigated (figure \ref{fig:memcellLoss}).

@@

This circuit is pretty straight forward, when the input enable pin is high (up to $V_{dd}$), then the first switch is open and the capacitor is being charged, if it is low, then the switch is closed and the capacitor keeps the voltage and thus the analog data. When the output enable is high, the buffer (appendix \ref{apsec:buffer}) forwards the voltage stored in the capactor to the output pin without emptying the capacitor.

>>>>

The circuit is shown in \cref{fig:memcellCircuit}. The value/voltage is trapped in the capacitor using \ac{CMOS} switches.

@@

The cirucit has a two \ac{CMOS} switches design to avoid voltage leakage through the swicthes. The system has voltage leakage when only one \ac{CMOS} swicth, and thus leads to a large memory leak. This is due to the high voltage difference between the two sides of the \ac{CMOS} swicth. Using two \ac{CMOS} switches allows for this difference to be mitigated (\cref{fig:memcellLoss}).

@@

This circuit is pretty straight forward, when the input enable pin is high (up to $V_{dd}$), then the first switch is open and the capacitor is being charged, if it is low, then the switch is closed and the capacitor keeps the voltage and thus the analog data. When the output enable is high, the buffer (\cref{apsec:buffer}) forwards the voltage stored in the capactor to the output pin without emptying the capacitor.
